Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-01 submission/NatCom_appendix.tex
tables 7,8,9 autogenerated

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.79 &  0.63 & \textbf{0.88} & 0.86 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.46 \\
 imagenet-1k & DLA  & 0.11 &  \textbf{0.65} & 0.40 & 0.36 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$RMSE$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.79 &  0.63 & \textbf{0.88} & 0.86 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.46 \\
 imagenet-1k & DLA  & 0.11 &  \textbf{0.65} & 0.40 & 0.36 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$R^{2}$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:R2results}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.77 &  0.74 & \textbf{0.88} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.67 &  \textbf{0.79} & 0.66 & 0.66 \\
 imagenet-1k & PreResNet  & 0.65 &  0.54 & \textbf{0.87} & 0.87 \\
 imagenet-1k & ShuffleNet  & 0.39 &  0.09 & \textbf{0.85} & 0.82 \\
 imagenet-1k & VGG  & \textbf{0.82} &  0.76 & 0.52 & 0.61 \\
 imagenet-1k & DLA  & 0.51 &  \textbf{0.82} & 0.78 & 0.69 \\
 imagenet-1k & HRNet  & 0.56 &  0.44 & \textbf{0.61} & 0.61 \\
 imagenet-1k & DRN-C  & \textbf{0.90} &  0.81 & 0.90 & 0.90 \\
 imagenet-1k & SqueezeNext  & 0.47 &  -0.33 & \textbf{0.73} & 0.73 \\
 imagenet-1k & ESPNetv2  & 0.00 &  0.80 & \textbf{1.00} & 1.00 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.33} &  0.33 & 0.33 & 0.33 \\
 imagenet-1k & SqueezeNet  & 0.33 &  0.00 & \textbf{0.67} & 0.67 \\
 imagenet-1k & IGCV3  & \textbf{1.00} &  0.00 & 1.00 & 1.00 \\
\hline
 cifar-10 & ResNet  & 0.64 &  0.64 & \textbf{0.71} & 0.71 \\
 cifar-10 & DIA-ResNet  & 0.79 &  0.50 & \textbf{0.86} & 0.79 \\
 cifar-10 & SENet  & 0.74 &  \textbf{0.95} & 0.95 & 0.95 \\
\hline
 cifar-100 & ResNet  & \textbf{0.64} &  0.57 & 0.64 & 0.64 \\
 cifar-100 & DIA-ResNet  & \textbf{0.93} &  0.43 & 0.93 & 0.93 \\
 cifar-100 & SENet  & \textbf{1.00} &  1.00 & 1.00 & 1.00 \\
 cifar-100 & WRN  & \textbf{0.67} &  -0.67 & 0.00 & 0.00 \\
\hline
 svhn & ResNet  & \textbf{0.81} &  0.71 & 0.81 & 0.81 \\
 svhn & DIA-ResNet  & \textbf{0.86} &  0.86 & 0.57 & 0.57 \\
 svhn & SENet  & \textbf{1.00} &  1.00 & 0.67 & 0.67 \\
 svhn & WRN  & -0.33 &  -0.33 & \textbf{0.67} & 0.67 \\
 svhn & ResNeXt  & \textbf{0.67} &  0.67 & 0.33 & 0.33 \\
\hline
 cub-200-2011 & ResNet  & \textbf{1.00} &  1.00 & -0.33 & -0.33 \\
 cub-200-2011 & SENet  & \textbf{0.87} &  0.87 & -0.20 & -0.20 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{Kendall-$\tau$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:KTresults}
\end{table}

>>>>

%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ImageNet 1K]{
%%        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
%%        \label{fig:imagenet1k-alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 10 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
%%        \label{fig:cifar10.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CIFAR 100 ]{
%%        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
%%        \label{fig:cifar100.alpha}
%%    }
%%    \qquad
%%    \subfigure[ SVHN ]{
%%        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
%%        \label{fig:svhn.alpha}
%%    }
%%    \qquad
%%    \subfigure[ CUB 200 ]{
%%        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
%%        \label{fig:cub200.alpha}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
%%            }
%%    \label{fig:DSalphas}
%%\end{figure}
%%
%% 
%%\begin{figure}[t]
%%    \centering
%%    \subfigure[ ResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_01}
%%    }
%%    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_02}
%%    }
%%    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_03}
%%    }
%%    \subfigure[ ResNeXt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_04}
%%    }
%%    \subfigure[ WRN ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_05}
%%    }
%%    \subfigure[ DLA ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_06}
%%    }
%%    \subfigure[ PreResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_07}
%%    }
%%    \subfigure[ ProxylessNAS ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_08}
%%    }
%%    \subfigure[ VGG/BN-VGG ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_09}
%%    }
%%    \subfigure[ IGCV3 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_10}
%%    }
%%    \subfigure[ EfficientNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_11}
%%    }
%%    \subfigure[ SqueezeNext/SqNxt ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_12}
%%    }
%%    \subfigure[ ShuffleNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_13}
%%    }
%%    \subfigure[ DRN-C/DRN-D ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_14}
%%    }
%%    \subfigure[ ESPNetv2 ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_15}
%%    }
%%    \subfigure[ HRNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_16}
%%    }
%%    \subfigure[ SqueezeNet/SqueezeResNet ]{
%%        \includegraphics[width=2.7cm]{img/hex.png}
%%        \label{fig:ARCHalphas_17}
%%    }
%%    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
%%            }
%%    \label{fig:ARCHalphas}
%%\end{figure}
\input{table_RMSE.tex}
\input{table_R2.tex}
\input{table_Ktau.tex}
